Brownian Dynein Model

### 2015-08-06 latex/derivation.tex
Add changes to derivation.tex from Mathematica verification.

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{t}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{s}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) \\
  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi)
\end{align}

\begin{align}
  Y_{bl} &= 0 \\
  Y_{ml} &= Y_{bl}+L_{t}\sin(\Theta_{bl}) \\
  Y_{t}  &= Y_{ml}+L_{s}\sin(\Theta_{ml}) \\
  Y_{mr} &= Y_{t} +L_{s}\sin(\Theta_{mr}-\pi) \\
  Y_{br} &= Y_{mr}+L_{t}\sin(\Theta_{br}-\pi)
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} \\
  \dot{X}_{t } &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

\begin{align}                                                                          
  \dot{Y}_{bl} &= 0 \\                                                        
  \dot{Y}_{ml} &= \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} \\
  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
\end{align}

\begin{align}                                                                               
  \dot{Y}_{bl} &= 0 \\                                                               
  \dot{Y}_{ml} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
\end{align}

@@

\section{Expanded Brownian Equations}

\begin{align}
  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
\end{align}

\begin{align}
  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
\end{align}

@@

\begin{align}
  L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) - R_{xml} \\
  L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) - R_{xt } \\
  L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) - R_{xmr} 
\end{align}

\begin{align}
  \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) - R_{yml}\\
  \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) - R_{yt } \\
  \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) - R_{ymr} 
\end{align}

@@

\begin{align}  
  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  \dot{X}_{t}  &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{ml} &= \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  \dot{Y}_{t}  &= \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
\end{align}

@@

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) =
\dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{multline}

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) =
\dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{multline}

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) =
\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
+ \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{equation}

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) = 
\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{equation}

>>>>

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{s}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} +L_{t}\cos(\Theta_{mr}-\pi) = X_{t} + \mn L_{t}\cos(\Theta_{mr}) \\
  X_{br} &= X_{mr}+L_{s}\cos(\Theta_{br}-\pi) = X_{mr}+ \mn L_{s}\cos(\Theta_{br})
\end{align}

\begin{align}
  Y_{bl} &= 0 \\
  Y_{ml} &= Y_{bl}+L_{s}\sin(\Theta_{bl}) \\
  Y_{t}  &= Y_{ml}+L_{t}\sin(\Theta_{ml}) \\
  Y_{mr} &= Y_{t} +L_{t}\sin(\Theta_{mr}-\pi) = Y_{t} + \mn L_{t}\sin(\Theta_{mr}) \\
  Y_{br} &= Y_{mr}+L_{s}\sin(\Theta_{br}-\pi) = Y_{mr}+ \mn L_{s}\sin(\Theta_{br})
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{X}_{t } &= \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\begin{align}                                                                          
  \dot{Y}_{bl} &= 0 \\                                                        
  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{X}_{t } &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{X}_{br} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\begin{align}                                                                               
  \dot{Y}_{bl} &= 0 \\                                                               
  \dot{Y}_{ml} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
\end{align}

@@

%Unnecessary section commented out
\begin{comment}
\section{Expanded Brownian Equations}

\begin{align}
  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
\end{align}

\begin{align}
  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
\end{align}

@@

\begin{align}
  L_{s}\sin(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) - R_{xml} \\
  L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) - R_{xt } \\
  L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) - R_{xmr} 
\end{align}

\begin{align}
  \mn L_{s}\cos(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  \mn L_{t}\cos(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) - R_{yml}\\
  \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) - R_{yt } \\
  \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) - R_{ymr} 
\end{align}
\end{comment}

@@

\begin{align}  
  \dot{X}_{ml} &= \dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  \dot{X}_{t}  &= \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
\end{align}

@@

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) =
\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) =
\dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) =
\dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
+ \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{equation}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) = 
\dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{equation}%Fix'd
